Carp\'{e} Data: Supporting Serendipitous Data Integration in Personal Information Management

### 2012-09-18 chi2012.tex
minor changes

At a high level, the overall goal of DataPalette was to empower end-users to mix arbitrary structured data feeds on-the-fly while solving their particular information task(s) - be them sense-making or decision-making related - in order to more effectively accomplish these tasks.  Unlike Mashup makers, including Yahoo Pipes!, the goal was to facilitate such integration without a need for an explicit separate mapping or integration step, which would detract from the overall usability or usefulness of the system by making people do something that did not immediately contribute to their resolving their need.

@@

% why? why were these tasks selected? can we drop in the phrase ``multi-dimensional subjective choice task'' and refer back to PS.1 to justify the choice of tasks?
We based our two tasks on these scenarios on choosing a university and picking a restaurant for a large social event, because in PS.1 the majority of people stated that they had used multiple websites for these tasks.  We used different two different variables for both tasks, where the restaurant was located (Glasgow and Cambridge) and which subject people choose (sport science and history).  The cities Glasgow and Cambridge were chosen because they are not geographically close to the participants, they are two heavily populated areas that have a choice of restaurants, and they contained detail data about the same restaurants on various review sites.  When deciding on which cities to use, we found that different areas favoured different review websites and places such as Hull had sets of disjoint sets of restaurant reviews.  We selected the top restaurants for on Tripadvisor and Yelp, because they were the top two websites people quoted for comparing reviews when travelling.  We selected the two courses for the university task at random from a list taken form the complete university guide\footnote{}, and selected the top six university for that subject because they provide a realistic shortlist and are comparable in terms of rankings and properties.   We selected a shortlist of six because it is typical for users to narrow down their options to a limited selection before analysing the details of their final choicesex

\subsubsection{Task preparation}
% how data was prepared for each of the tasks; exactly how the A condition was done (full screen DP in a web browser, no outside access to apps),  B condition and why
In order to prepare the data for our tasks, we identified websites that people commonly used for selecting universities and restaurants.  Once we had compiled the list of websites, we select the top most used six for each task.  We selected six because it enable us to scope our study, we found through two pilot studies that six data sources provided a sufficient challenge for users to explore the data and required them to use DP's main features.  We manually collected the data from the nine selected websites into jason files, and converted them to Microsoft Excel worksheets (which 40\% of the participants in PS.1 said that they used to compare data in).

@@

\subsection{Participant Recruitment}
We recruited participants through adverts posted near the University campus and e-mails to student mailing lists.  We screened participants to be at least 18 years of age, but did not filter or preferentially select participants based on any other criteria.  We took the first 20 that signed up and that successfully specified time slots that were available.   As described below in results, we ended up getting a large number of international students, who had varying proficiency in English.  Since all such participants had passed the requisite proficiency tests to enrol at University, we did not think this would substantially impact results.  Participants were offered a small gift certificate from an online retailer in exchange for their time.

\subsection{Experimental Setup}
The participants were given a standard desktop PC running MacOS X on a 22-inch monitor with a standard keyboard and mouse.  During the studies the Excel workbook and DP were initially set to full screen by default.  Each participant was asked to complete two tasks, one A and one B condition.  Each participant was given a maximum of 10 minutes to complete a task, but were told that if they finished earlier they could tell us and move on to the next condition.  In order to select which tasks the participant was given, we used a latin square to permutate the tasks and conditions.  In order to train the user on how to use our interface, they viewed a five-minute DataPalette tutorial video introducing its basic functionality, how to use histograms and maps, and linking instances.

@@

Twenty-six (26) participants responded, from which we selected the first 20.  Ten participants were female.  All of the participants spoke English, but 12 of them were non-native English speakers.  Seven were non-students, comprising University staff and alumni; out of the remaining 13, eight studied computer science and 5 studied other subjects.   On average, each study took 40 mins to complete.

The information in Table \ref{tbl:data} summarises the metrics that were captured of the trials for each participant. We analyse this data next.

@@

We used three metrics to measure task performance: time to completion; the number of factors used in the choice; and the number of candidates evaluated.

\subsubsection{Efficiency: Time taken}
Participants spent an average of 8.9 minutes performing the tasks overall, with condition A (DataPalette) taking slightly less time ($M=8.7$min, $SD=1.79$) per trial than condition B (the web browser/Excel interface) ($M=9.0$min; $SD=1.44$).  An ANOVA test of time taken by interface condition blocking by participant did not find interface use a significant predictor of task completion time. A comparison of times taken are visible in Figure \ref{fig:time}.

Although across trials, the restaurant selection task took on average slightly less time ($M=8.8$min,$SD=1.58$) than the university trials ($M=8.9$min,$SD=1.66$), the aforementioned ANOVA test found task type to not be a significant predictor.

@@

Since the tasks were subjective-choice, we could not evaluate the 'correctness' of people's answers.  However, to determine whether there was a difference in variability of answers between interface conditions, we histogrammed first choices for each trial, per task and dataset for both conditions, visible in  Figure \ref{fig:chosen_results}.  As can be seen there is considerable variability and no discernable difference in variability between conditions.

>>>>

At a high level, the overall goal of DataPalette was to empower end-users to mix arbitrary structured data feeds on-the-fly while solving their particular information task(s) - be them sense-making or decision-making related - in order to more effectively accomplish these tasks.  Unlike Mashup makers, including Yahoo Pipes!, the goal was to facilitate such integration without a need for an explicit separate mapping or integration step.  This would detract from the overall usability and usefulness of the system by requiring that users perform tasks that did not immediately contribute to their resolving their need.

@@

% why? why were these tasks selected? can we drop in the phrase ``multi-dimensional subjective choice task'' and refer back to PS.1 to justify the choice of tasks?
We based our two tasks on choosing a university and picking a restaurant for a large social event, because in PS.1 the majority of people stated that they had used multiple websites for these tasks.  We used different two different variables for both tasks, where the restaurant was located (Glasgow and Cambridge) and which subject people choose (sport science and history).  The cities Glasgow and Cambridge were chosen because they are not geographically close to the participants, they are two heavily populated areas that have a choice of restaurants, and they contained detail data about the same restaurants on various review sites.  When deciding on which cities to use, we found that different areas favoured different review websites and places such as Hull had sets of disjoint sets of restaurant reviews.  We selected the top restaurants for on Tripadvisor and Yelp, because they were the top two websites people quoted for comparing reviews when travelling.  We selected the two university courses at random from a list taken form the complete university guide\footnote{}, and selected the top six university for that subject because they provide a realistic shortlist and are comparable in terms of rankings and properties.   We selected a shortlist of six because it is typical for users to narrow down their options to a limited selection before analysing the details of their final choice.

\subsubsection{Task preparation}
% how data was prepared for each of the tasks; exactly how the A condition was done (full screen DP in a web browser, no outside access to apps),  B condition and why
In order to prepare the data for our tasks, we identified websites that people commonly used for selecting universities and restaurants.  Once we had compiled the list of websites, we select the top most used six for each task.  We selected six because it enable us to scope our study, we found through two pilot studies that six data sources provided a sufficient challenge for users to explore the data and required them to use DP's main features.  We manually collected the data from the nine selected websites into jason files, and converted them to Microsoft Excel worksheets (which 40\% of the participants in PS.1 said that had previously used to compare data).

@@

\subsection{Participant Recruitment}
We recruited participants through adverts posted near the University campus and e-mails to student mailing lists.  We screened participants to be at least 18 years of age, but did not filter or preferentially select participants based on any other criteria.  We took the first 20 that signed up and that successfully specified time slots that were available.   As described below in results, we ended up getting a large number of international students, who had varying proficiency in English.  Since all such participants had passed the requisite proficiency tests to enrol at University, we did not think this would substantially impact results.  Participants were offered a small gift certificate from an online retailer for their time.

\subsection{Experimental Setup}
The participants were given a standard desktop PC running MacOS X on a 22-inch monitor with a standard keyboard and mouse.  During the studies the Excel workbook and DP were initially set to full screen.  Each participant was asked to complete two tasks, one A and one B condition.  Each participant was given a maximum of 10 minutes to complete a task, but were told that if they finished earlier they could tell us and move on to the next condition.  In order to select which tasks the participant was given, we used a latin square to permutate the tasks and conditions.  In order to train the user on how to use our interface, they viewed a five-minute DataPalette tutorial video introducing its basic functionality, how to use histograms and maps, and linking instances.

@@

Twenty-six (26) participants responded, from which we selected the first 20.  Ten participants were female.  All of the participants spoke English, but 12 of them were non-native English speakers.  Seven were non-students, comprising University staff and alumni; out of the remaining 13, eight studied computer science and 5 studied other subjects.   On average, each study took 40 mins to complete.  The information in Table \ref{tbl:data} summarises the metrics that were captured of the trials for each participant. We analyse this data next.

@@

The following four sections describes the metrics we used to measure task performance.
%We used three metrics to measure task performance: time to completion; the number of factors used in the choice; and the number of candidates evaluated.

\subsubsection{Efficiency: Time taken}
Participants spent an average of 8.9 minutes performing the tasks, with our interface, condition A, taking slightly less time ($M=8.7$min, $SD=1.79$) per trial than condition B ($M=9.0$min; $SD=1.44$).  An ANOVA test of time taken by interface condition blocking by participant did not find interface use a significant predictor of task completion time (shown in Figure \ref{fig:time}).  Although across trials, the restaurant selection task took on average slightly less time ($M=8.8$min,$SD=1.58$) than the university trials ($M=8.9$min,$SD=1.66$), the aforementioned ANOVA test found task type to not be a significant predictor.

@@

Since the tasks were subjective-choice, we could not evaluate the 'correctness' of people's answers.  However, to determine whether there was a difference in variability of answers between interface conditions, we plotted their choice on a histogram for each trial, per task and dataset for both conditions, visible in Figure \ref{fig:chosen_results}.  As can be seen there is considerable variability and no discernible difference in variability between conditions.
